% 25 Mar 2014 : GWA : Goal is 1.5 pages including scenarios and a taxonomy of
% different types of mocking.

\section{Motivation}
\label{sec-motivation}

Second only to battery life, recent studies show that privacy is one of
today's smartphone users' top concerns with their
devices~\cite{truste-privacy}. Despite the high demand for free ad-driven
apps, 43\% of users are \textit{not} willing to share personal information with
a company in exchange for a free app.  Fortunately, smartphone user privacy
receives significant attention from academia and industry. Protecting users'
privacy is a worthwhile goal, but ironically, we believe privacy itself may be
part of the smartphone privacy problem.

The reason is that understanding privacy implications requires smartphone users
to answer difficult questions. If I install and use this app, what will it be
able to learn about me? Is all of the data this app collects really necessary?
Is this app using my data for legitimate reasons? Companies are spending billions of dollars
to better profile their users through data analysis algorithms and few, if any,
have a business interest in releasing how their algorithms work or what they
know about their users. Even with new tools to determine what and how much data
is collected on a smartphone, it is still unknown how that data is being used.

Obviously users can always choose not to use apps with which they feel
uncomfortable, but that is not an ideal solution if they are interested in a
particular app's functionality. There are efforts out there to better protect
users through safer app marketplaces by preventing distribution of malicious apps that
only want to misuse the permission-protected data, but even non-malicious apps
can be problematic. For the average user who reads email, browses the web,
takes pictures and so on, their privacy may still be at risk to legitimate apps
with legitimate data collection. At this point, users have two very
unattractive options: removing useful apps or not using their smartphone
at all.

To further investigate smartphone user thoughts on privacy, we distributed an
IRB-approved survey---asking about their thoughts on smartphones knowing their
address, friends, activity level, income and weight---to students, faculty and
staff of the University at Buffalo\footnote{We discuss this survey in more
detail in our concurrent publication submitted to HotPlanet 2014.}. No
incentives were provided for completing  the  survey,  and all  respondents
were  required to indicate consent before proceeding to the questions.  Over
four days, we recorded 91 responses. First,  we  found  that respondents  to be
reasonably suspicious of what apps might know about them, with 52\% indicating
that  an app  might  know  at  least  one personal attribute  to a  level  that
we marked  as  unreasonable  today---such as income and weight---but  only 18\%
indicating that  apps might know two attributes of unreasonable levels.  And
when asked about mocking,  of the 91 users that  completed  the  survey, 82\%
wanted  to mock  at least one attribute and 60\% wanted to mock two, with
mocking users requesting an average of 2.6 mocking attributes each. Our results
show that users are concerned with what their smartphone may know about them,
and users are interested in the ability to better control their private data on
their devices.

It is at that point that mocking has a role to play. In contrast to the
uncertainties caused by privacy, mocking provides control. Instead of
wondering what information an employer required app collects on a
bring-your-own-device, users can set up mocking objectives that
ensure that it appears that they work regular hours. Instead of wondering
which apps might be collecting information about their drinking habits, users
can set up mocking objectives to conceal their visits to bars. We believe
that this type of control over their digital identities will be appealing
to users, since it is similar to the control they already have when
interacting with other online services. While Facebook users know that
Facebook is collecting data about them, they also exercise control over the
impression they create. \PocketMocker{} provides smartphone users with the
same control over their smartphone-derived digital identities.


\subsection{Mocking Scenarios and Types}

Consider these four scenarios:

\begin{itemize}

\item Bob wants to appear more active. Instead of taking real walks, his
smartphone can mock a walk while he sits at his desk during work hours.

\item Alice wants to appear more healthy. While eating at a burger joint, her
smartphone can mock a visit to the local vegetarian restaurant.

\item Teenager Jerry is monitored by a smartphone app installed by his parents
to ensure he is not out past curfew. He can stay out later-than-allowed with
his friends, while his smartphone mocks his location to return home on time.

\item Carol is monitored by a smartphone app setup by her employer to track
attendance and working hours. Despite leaving for a latte with a friend, her
smartphone can mock her still sitting at her desk.

\end{itemize}

These examples show that there is indeed a difference between \textit{privacy}
and \textit{mocking}. The above objectives are concerned with privacy, but
cannot be achieved by making data more private, thus this is where mocking can
have a role to better protect users. In Jerry and Carol's case, the apps could
be removed, but the installing party would notice; or in some instances,
uninstalling an app would also mean forfeiting certain rewards for using it,
such is the case with most ``gamified'' apps, assuming Bob and Alice are using
such an app. In all cases, removing or disabling an app is not an attractive or
possible option.

These scenarios also illustrate examples of two different types of
mocking: record-and-replay and time shifting.

\subsubsection{Record and Replay mocking:\space}

In record-and-replay mocking the objective can be directly embedded in the
mocked activity. Bob's recorded walk inherently makes him appear more active
the more he replays it, and Alice's visit to the healthy restaurant makes her
appear more healthy. In other cases, the objective can also be to obscure
another activity, replacing something undesirable with something desirable.
As Alice replays the desirable visit to the healthy restaurant, it provides
cover for her undesirable visit to the unhealthy restaurant.

In other cases, \PocketMocker{} users may simply want to have their smartphones
mock staying in one place while they in fact go to another, as in
Carol's example when she visits with her friend instead of working. While this
behavior is similar to that offered by traditional record-and-replay systems,
this variant requires \PocketMocker{} be able to extend or loop a recorded
session for an indefinite amount of time in order to mask an activity and to
ensure time continuity between the mocking trace and the user's real activity.

\subsubsection{Time shift mocking:\space}

In time-shift mocking, a user wants it to appear that something that happened
at one time actually happened at another. Time shifting can move an activity
later or earlier, the later exemplified by Jerry's example where he wants his
parents to think that he arrived home punctually. We call the former
\textit{forward} time shifting and the latter \textit{backward}.

While conceptually similar, forward and backward time shifting create
different design requirements. Backward time shifting---making something that
happens in the future appear to happen earlier---requires either being able
to synthesize a transition from the current context to the mocked context or
having a pre-recorded trace that accomplishes the same thing. In Jerry's
example, in order to look like he returned home early, his smartphone must
either be able to create a location transition from his current location to
home, or he must have previously recorded this transition.

Forward time shifting is somewhat easier, since the user's real transition can
be recorded, saved, and then held until the user is ready to replay it at a
later point in time. If Carol wants to leave work early, she can record her
transition to home but then delay it for several hours until the working day
is over. Like record-and-replay, however, this type of mocking also requires
\PocketMocker{} to be able to dwell in a particular context while the user
moves to another by looping a portion of a pre-recorded context.
