\begin{framed}
  \textbf{What can data collected by your smartphone reveal about you?}

  {\small The questions below assess how much you think your phone is able to
    determine about you without asking. All the questions assume that you
    have installed the application and granted it the permissions it
  requested.}
  \vspace*{-5pt}

  \begin{itemize}[leftmargin=15pt,noitemsep]
    \item \uline{Without asking, what could an application determine about} your
      yearly income?
      \begin{itemize}[leftmargin=15pt,noitemsep]
        \item An application could predict my income exactly, to within \$1 /
          year.
        \item An application could predict my income to within \$100 / year.
        \item An application could predict my income to within \$10,000 / year.
        \item An application could not determine anything about my income
          level.
      \end{itemize}
    \item $\ldots$ your weight?
    \item $\ldots$ your social network?
    \item $\ldots$ your activity level?
    \item $\ldots$ where you live?
  \end{itemize}

  \vspace*{-10pt}

\end{framed}

\begin{framed}
  \textbf{What are you comfortable with applications knowing about you?}

  {\small The questions below assess how comfortable you are with smartphone
    application being able to determine the same things about you we asked
    about in the first section. \textbf{Please indicate your comfort level
  between not comfortable at all (1) and completely comfortable (5).}}
  \vspace*{-5pt}

  \begin{itemize}[leftmargin=15pt,noitemsep]
    \item \uline{How comfortable are you with smartphone applications
      knowing} your yearly income?
    \item $\ldots$ your weight?
    \item $\ldots$ about your social network?
    \item $\ldots$ your activity level?
    \item $\ldots$ where you live?
  \end{itemize}
  \vspace*{-10pt}

\end{framed}

\begin{framed}
  \textbf{Would you like to alter what your smartphone knows about you?}

  {\small These questions assess your interest in altering what your
    smartphone knows about you. Assume that a system exists that would allow
  you to change the qualities as indicated by the questions.}
  \vspace*{-5pt}

  \begin{itemize}[leftmargin=15pt,noitemsep]
    \item \uline{If a smartphone application could accurately determine} my income
      level 
      \begin{itemize}[leftmargin=15pt,noitemsep]
        \item I would like to appear to have a lower yearly income than I
          actually do.
        \item I would like to appear to have a higher yearly income than I
          actually do.
        \item I am comfortable revealing my true income level to the
          application.
      \end{itemize}
    \item $\ldots$ my weight
    \item $\ldots$ my social network
    \item $\ldots$ my activity level
    \item $\ldots$ where I live
  \end{itemize}
  \vspace*{-10pt}

\end{framed}
